Experiences with Planning for Natural Language Generation

### 2008-06-23 trunk/Papers/experiences/experiences.tex
added abstract

\begin{abstract}
We investigate the application of modern planning techniques to domains
arising from problems in natural language generation (NLG). In particular,
we consider two novel NLG-inspired planning problems, the sentence
generation domain and the GIVE (``Generating Instructions in Virtual
Environment'') domain, and investigate the efficiency of FF and SGPLAN in
these domains. We also compare our results against an ad-hoc implementation
of GraphPlan in Java. Our results are mixed. While modern planners are able
to quickly solve many moderately-sized instances of the NLG problems, the
overall planning time is dominated by grounding, rather than search, which
has a pronounced effect on our domains which require relatively short plans
in large universes.

We offer these domains as challenges for the planning community.
\end{abstract}

>>>>

\begin{abstract}
We investigate the application of modern planning techniques to domains
arising from problems in natural language generation (NLG). In particular,
we consider two novel NLG-inspired planning problems, the sentence
generation domain and the GIVE (``Generating Instructions in Virtual
Environment'') domain, and investigate the efficiency of FF and SGPLAN in
these domains. We also compare our results against an ad-hoc implementation
of GraphPlan in Java. Our results are mixed. While modern planners are able
to quickly solve many moderately-sized instances of our problems, the
overall planning time is dominated by the grounding step that these
planners perform (rather than search). This has a pronounced effect on our
domains which require relatively short plans in large universes.  We share
our experiences and offer these domains as challenges for the planning
community.
\end{abstract}
